Argennon: A Scalable Smart Contract Platform

### 2021-07-26 tex/sections/avm.tex
Add identifier matching algorithm
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Execution sessions are separate sessions of executing smart contract's code by the Argennon Virtual Machine.
Every execution session starts with a single method invocation, but does not necessarily end with
that method invocation. During an execution session additional method invocations could be scheduled,
which will be executed after the initial method completes.

@@

The Argennon virtual machine does not have a fixed word size. Any instruction of the AVM has
its specific word size, and the addressable memory areas are byte addressable.

@@

All these identifiers are \emph{prefix codes}, and hence can be represented by
\emph{prefix trees}\footnote{Also called tries.}. The Argennon has three primitive prefix trees:
\emph{applications, accounts} and \emph{local}. Any identifier in Argennon is a
prefix code built by using one or more of these prefix trees:
\begin{itemize}
    \item \texttt{applicationID} is a prefix code built by \emph{applications} prefix tree.
    \item \texttt{accountID} is a prefix code built by \emph{accounts} prefix tree. An \texttt{accountID} can
    not be \texttt{0x0} or \texttt{0x1}.
    \item \texttt{methodID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    a prefix code made by \emph{local} prefix tree: (\texttt{|} is the concatenating operator)
    \subitem \texttt{methodID = (applicationID|<local-prefix-code>)} .
    \item \texttt{chunkID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    an \texttt{accountID} to a prefix code made by \emph{local} prefix tree:
    \subitem \texttt{chunkID = (applicationID|accountID)} or
    \subitem \texttt{chunkID = (applicationID|0x0|<local-prefix-code>)} or
    \subitem \texttt{chunkID = (applicationID|0x1|accountID|<local-prefix-code>)} .
\end{itemize}

@@

One important property of prefix identifiers is that while they have variable and unlimited length, they are
uniquely extractable from any sequence. Assume that we have a string of digits in base $\beta$, we
know that $k$ first digits belong to an Argennon's identifier, but we don't know the value of $k$.
Algorithm~\ref{alg:prefix_id} can be used to extract the prefixed identifier uniquely. Also, we can apply this algorithm
multiple times to extract a composite identifier, for example \texttt{chunkID}, from a sequence.

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
    {Txns}{$T$}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{A sequence of $n$ digits in base $\beta$: $d_{1}d_{2}\dots d_{n}$ \newline
    A prefix tree: $<A^{(1)},A^{(2)},A^{(3)},\dots>$}
    \Output{Valid identifier prefix of the sequence.}
    \BlankLine
    \For{$i = 1$ \KwTo $n$}
    {
        \If{$(0.d_{1}d_{2}\dots d_{i})_\beta < A^{(i)}$}
        {
            \KwRet{$d_{1}d_{2}\dots d_{i}$}\;
        }
    }
    \KwRet{NIL}\;
    \caption{Finding a prefixed identifier}\label{alg:prefix_id}
\end{algorithm}

@@

>>>>

Execution sessions are separate sessions of executing smart contract's code by the Argennon Virtual Machine.
Every execution session starts with a single method invocation, but does not necessarily end with
that method invocation. During an execution session additional method invocations could be scheduled,
which will be executed after the initial method invocation completes.

@@

The Argennon Virtual Machine does not have a fixed word size. Any instruction of the AVM has
its specific word size, and the addressable memory areas are byte addressable.

@@

All these identifiers are \emph{prefix codes}, and hence can be represented by
\emph{prefix trees}\footnote{Also called tries.}. The Argennon has three primitive prefix trees:
\emph{applications, accounts} and \emph{local}. Any identifier in Argennon is a
prefix code built by one or more of these prefix trees:
\begin{itemize}
    \item \texttt{applicationID} is a prefix code built by \emph{applications} prefix tree.
    \item \texttt{accountID} is a prefix code built by \emph{accounts} prefix tree. An \texttt{accountID} can
    not be \texttt{0x0} or \texttt{0x1}.
    \item \texttt{methodID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    a prefix code made by \emph{local} prefix tree: (\texttt{|} is the concatenating operator)
    \subitem \texttt{methodID = (applicationID|<local-prefix-code>)} .
    \item \texttt{chunkID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    an \texttt{accountID} to a prefix code made by \emph{local} prefix tree:
    \subitem \texttt{chunkID = (applicationID|accountID)} or
    \subitem \texttt{chunkID = (applicationID|0x0|<local-prefix-code>)} or
    \subitem \texttt{chunkID = (applicationID|0x1|accountID|<local-prefix-code>)} .
\end{itemize}

@@

One important property of prefix identifiers is that while they have variable and unlimited length, they are
uniquely extractable from any sequence. Assume that we have a string of digits in base $\beta$, we
know that $k$ first digits belong to an Argennon identifier, but we don't know the value of $k$.
Algorithm~\ref{alg:prefix_id} can be used to extract the prefixed identifier uniquely. Also, we can apply this algorithm
multiple times to extract a composite identifier, for example \texttt{chunkID}, from a sequence.

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}[t]
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{A sequence of $n$ digits in base $\beta$: $d_{1}d_{2}\dots d_{n}$ \newline
    A prefix tree: $<0,A^{(1)},A^{(2)},A^{(3)},\dots>$}
    \BlankLine
    \Output{Valid identifier prefix of the sequence.}
    \BlankLine
    \For{$i = 1$ \KwTo $n$}
    {
        \If{$(0.d_{1}d_{2}\dots d_{i})_\beta < A^{(i)}$}
        {
            \KwRet{$d_{1}d_{2}\dots d_{i}$}\;
        }
    }
    \KwRet{NIL}\;
    \caption{Finding a prefixed identifier}\label{alg:prefix_id}
\end{algorithm}

When we have a prefixed identifier, and we want to know if a sequence of digits is marked by that identifier,
we use Algorithm~\ref{alg:match_id} to match the prefixed identifier with the start of the sequence. The matching
can be done with only three comparisons and an invalid prefixed identifier can also be detected.

@@

\begin{algorithm}[h]
    \DontPrintSemicolon
    \SetKwData{Id}{$id$}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{A prefixed identifier in base $\beta$ with $n$ digits: $\Id=a_{1}a_{2}\dots a_{n}$ \newline
    A sequence of digits in base $\beta$: $d_{1}d_{2}d_{3}\dots $ \newline
    A prefix tree: $<0,A^{(1)},A^{(2)},A^{(3)},\dots>$
    }
    \BlankLine
    \Output{$TURE$ if and only if the identifier is valid and the sequence starts with the identifier.}
    \BlankLine
    \If{$(0.a_{1}\dots a_{n})_\beta = (0.d_{1}\dots d_{n})_\beta$}
    {
        \If{$A^{(n-1)} \leq (0.a_{1}a_{2}\dots a_{n})_\beta < A^{(n)}$}
        {
            \KwRet{TRUE}\;
        }
    }
    \KwRet{FALSE}\;
    \caption{Matching a prefixed identifier}\label{alg:match_id}
\end{algorithm}
